Contracts for Contracts

### 2022-12-13 paper.tex
misc

\subsubsection*{\textbf{Behavioral Contracts for Smart Contracts}}
Behavioral contracts provide a mechanism for programmers to specify assumptions
and guarantees of software components. The specified assumptions and guarantees
will be monitored and reported when violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
Design-by-Contract methodology \cite{DBLP:conf/tools/Meyer98a}, behavioral
contracts have been widely adopted in Java, Haskell, C\#, Python, Racket, etc. \todo{cite}

@@

At the conceptual level, behavioral contracts is complementary to smart
contracts, in this sense that they are both agreement -- between software
components for the former, and between transactional parties for the later.
Thus, the two ``contracts'' indeed mean the same thing but just different levels
of enforcement.

>>>>

\subsubsection*{\textbf{Behavioral Contracts for Smart Contracts}}
Behavioral contracts provide a mechanism for programmers to specify assumptions
and guarantees of software components. The specified assumptions and guarantees
will be monitored and reported when violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
Design-by-Contract methodology \cite{DBLP:conf/tools/Meyer98a}, behavioral
contracts have been widely adopted in Java, Haskell, C\#, Python, Racket,
Elixir \cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \todo{cite}

@@

At the conceptual level, behavioral contracts is complementary to smart
contracts, in the sense that they are both agreement -- between software
components for the former, and between transactional parties for the later.
Thus, the two terms ``contract'' indeed mean the same thing but just different
levels of enforcement.
